|

### 2022-11-03 ms/ms.Rmd
<edit ms>

\begin{figure}\centering
\includegraphics[width=\linewidth]{figs/gpa.csize.png}
\caption{Results of a, generalised Procrustes analysis; and b, boxplot of centroid sizes for Chimu bottles and jars.}
\label{fig:gpa}
\end{figure}

@@

\begin{figure}\centering
\includegraphics[width=\linewidth]{figs/pca-warp-botjar.jpg}
\caption{PCA summarizing shape variation for Chimu bottles and jars. }
\label{fig:pca}
\end{figure}

>>>>

\begin{figure}\centering
\includegraphics[width=\linewidth]{figs/gpa.csize.png}
\caption{Results of a, generalised Procrustes analysis; and b, boxplot of centroid sizes for Chimu bottles (gray) and jars (orange).}
\label{fig:gpa}
\end{figure}

@@

\begin{figure}\centering
\includegraphics[width=\linewidth]{figs/pca-warp-botjar.jpg}
\caption{PCA summarizing shape variation for Chimu bottles (gray) and jars (orange). }
\label{fig:pca}
\end{figure}
